---
title: "ClassActivity1"
author: "Shuangmu Feng"
date: "9/20/2018"
output: html_document
---
### Instructions
  
1. Open a new R Markdown file, please write and run all your commands from within the R Markdown document  
2. Delete the contents of the Markdown file and insert a new code block
3. Load the libraries  `tidyr` and `dplyr`
```{r}
library(tidyr)
library(dplyr)
```

4. Create a data frame from the `swirl-data.csv` file called `DF1`

The variables are:

`course_name` - the name of the R course the student attempted  
`lesson_name` - the lesson name  
`question_number` - the question number attempted
`correct` - whether the question was answered correctly  
`attempt` - how many times the student attempted the question  
`skipped` - whether the student skipped the question  
`datetime` - the date and time the student attempted the question  
`hash` - anonymyzed student ID  
```{r}
DF1 <- read.csv("swirl-data.csv", header = TRUE)
```


5. Create a new data frame that only includes the variables `hash`, `lesson_name` and `attempt` called `DF2`
```{r}
DF2 <- select(DF1, hash, lesson_name, attempt)
```


6. Use the `group_by` function to create a data frame that sums all the attempts for each `hash` by each `lesson_name` called `DF3`
```{r}
  DF3 <- group_by(DF2, hash, lesson_name) %>% summarize(attempt = sum(attempt))
```


7. On a scrap piece of paper draw what you think `DF3` would look like if all the lesson names were column names
```{r}

```


8. Convert `DF3` to this format  
```{r}

```


9. Create a new data frame from `DF1` called `DF4` that only includes the variables `hash` and `correct`
```{r}
DF4 <- select(DF1, hash, correct)
```


10. Convert the `correct` variable so that `TRUE` is coded as the **number** `1` and `FALSE` is coded as `0`  
```{r}
DF4$correct <- as.numeric(DF4$correct == "TRUE")
v zsioproiud=-0954
!```


11. Create a new data frame that called `DF4` that provides a mean score for each student
```{r}
DF4 <- group_by(DF4, hash) %>% summarize(score = mean(correct, na.rm = TRUE))
```


12. **Extra credit** Convert the `datetime` variable into month-day-year format and create a new data frame (`DF5`) that shows the average correct for each day
```{r}
class(DF1$datetime) = c('POSIXt','POSIXct')
DF1$datetime <- as.Date(DF1$datetime)
DF1$datetime <- format(DF1$datetime, "%m-%Y-%d")
DF1$datetime
DF1$correct <- as.numeric(DF1$correct == "TRUE")
DF5 <- group_by(DF1, datetime, hash) %>% summarize(correct = mean(correct, na.rm = TRUE))


```

